Cloudbreak: A MapReduce Algorithm for Detecting Genomic Structural Variation

### 2013-05-29 manuscript/NA18507DeletionAndInsertionPredsBySize.table.brew.tex
updates to NM manuscript

\multirow{4}{*}{\begin{sideways}Insertions\end{sideways}} & Total Number & & & <%= format(totalIns['40-100bp'], big.mark=",") %> & <%= format(totalIns['101-250bp'], big.mark=",") %> & <%= format(totalIns['251-500bp'], big.mark=",") %> & <%= format(totalIns['501-1000bp'], big.mark=",") %> \\

@@

& Cloudbreak & <%= printPredTableValueFromList('Cloudbreak', insPrecision) %> & <%= printPredTableValueFromList('Cloudbreak', insRecall) %> & <%= printPredTableCell(insPreds, exInsPreds, 'Cloudbreak', '40-100bp') %>  & <%= printPredTableCell(insPreds, exInsPreds, 'Cloudbreak', '101-250bp') %> &  <%= printPredTableCell(insPreds, exInsPreds, 'Cloudbreak', '251-500bp') %> & <%= printPredTableCell(insPreds, exInsPreds, 'Cloudbreak', '501-1000bp') %> \\ 
& Breakdancer & <%= printPredTableValueFromList('Breakdancer', insPrecision) %> & <%= printPredTableValueFromList('Breakdancer', insRecall) %> & <%= printPredTableCell(insPreds, exInsPreds, 'Breakdancer', '40-100bp') %>  & <%= printPredTableCell(insPreds, exInsPreds, 'Breakdancer', '101-250bp') %> &  <%= printPredTableCell(insPreds, exInsPreds, 'Breakdancer', '251-500bp') %> & <%= printPredTableCell(insPreds, exInsPreds, 'Breakdancer', '501-1000bp') %> \\  
&  Pindel & <%= printPredTableValueFromList('Pindel', insPrecision) %> & <%= printPredTableValueFromList('Pindel', insRecall) %> & <%= printPredTableCell(insPreds, exInsPreds, 'Pindel', '40-100bp') %>  & <%= printPredTableCell(insPreds, exInsPreds, 'Pindel', '101-250bp') %> &  <%= printPredTableCell(insPreds, exInsPreds, 'Pindel', '251-500bp') %> & <%= printPredTableCell(insPreds, exInsPreds, 'Pindel', '501-1000bp') %>  \\ 

>>>>

\multirow{4}{*}{\begin{sideways}Insertions\end{sideways}} & Total Number & & & <%= format(totalIns['40-100bp'], big.mark=",") %> & <%= format(totalIns['101-250bp'], big.mark=",") %> & <%= format(totalIns['251-500bp'], big.mark=",") %> & <%= format(totalIns['501-1000bp'], big.mark=",") %> & 0 \\

@@

& Cloudbreak & <%= printPredTableValueFromList('Cloudbreak', insPrecision) %> & <%= printPredTableValueFromList('Cloudbreak', insRecall) %> & <%= printPredTableCell(insPreds, exInsPreds, 'Cloudbreak', '40-100bp') %>  & <%= printPredTableCell(insPreds, exInsPreds, 'Cloudbreak', '101-250bp') %> &  <%= printPredTableCell(insPreds, exInsPreds, 'Cloudbreak', '251-500bp') %> & <%= printPredTableCell(insPreds, exInsPreds, 'Cloudbreak', '501-1000bp') %>  & <%= printPredTableCell(insPreds, exInsPreds, 'Cloudbreak', '> 1000bp') %>  \\ 
& Breakdancer & <%= printPredTableValueFromList('Breakdancer', insPrecision) %> & <%= printPredTableValueFromList('Breakdancer', insRecall) %> & <%= printPredTableCell(insPreds, exInsPreds, 'Breakdancer', '40-100bp') %>  & <%= printPredTableCell(insPreds, exInsPreds, 'Breakdancer', '101-250bp') %> &  <%= printPredTableCell(insPreds, exInsPreds, 'Breakdancer', '251-500bp') %> & <%= printPredTableCell(insPreds, exInsPreds, 'Breakdancer', '501-1000bp')  %> & <%= printPredTableCell(insPreds, exInsPreds, 'Cloudbreak', '> 1000bp') %> \\  
&  Pindel & <%= printPredTableValueFromList('Pindel', insPrecision) %> & <%= printPredTableValueFromList('Pindel', insRecall) %> & <%= printPredTableCell(insPreds, exInsPreds, 'Pindel', '40-100bp') %>  & <%= printPredTableCell(insPreds, exInsPreds, 'Pindel', '101-250bp') %> &  <%= printPredTableCell(insPreds, exInsPreds, 'Pindel', '251-500bp') %> & <%= printPredTableCell(insPreds, exInsPreds, 'Pindel', '501-1000bp')  %> &  <%= printPredTableCell(insPreds, exInsPreds, 'Pindel', '> 1000bp')  %> \\ 
